
\documentclass[11pt, twoside]{article}

%% ---------------------------------------------------
%% 634format specifies the format of our reports
%% ---------------------------------------------------
\usepackage{634format}

%% ---------------------------------------------------
%% enumerate 
%% ---------------------------------------------------
\usepackage{enumerate}

%% ---------------------------------------------------
%% listings is used for including our source code in reports
%% ---------------------------------------------------
\usepackage{listings}
\usepackage{textcomp}
\usepackage{indentfirst}

%% ---------------------------------------------------
%% Packages for math environments
%% ---------------------------------------------------
\usepackage{amsmath}

%% ---------------------------------------------------
%% Packages for URLs and hotlinks in the table of contents
%% and symbolic cross references using \ref
%% ---------------------------------------------------
\usepackage{hyperref}

%% ---------------------------------------------------
%% Packages for using HOL-generated macros and displays
%% ---------------------------------------------------
\usepackage{holtex}
\usepackage{holtexbasic}
\input{commands}

%% ---------------------------------------------------
%% Package for a table that will break across pages
%% ---------------------------------------------------
\usepackage{longtable}

%% ---------------------------------------------------
%% Packages to bring the contents of other files in
%% ---------------------------------------------------
\usepackage{import}
\usepackage{moreverb}

%% ---------------------------------------------------
%% parameter "language" is set to "ML"
%% ---------------------------------------------------
\lstset{language=ML}

\makeindex


\title{Project 5}
\author{\textbf{Alfred Murabito}}
\date{\today}

\begin{document}
\maketitle{}

\newpage

\begin{abstract}
   \noindent{}This report details results for the following exercises
from \textit{Certified Security by Design Using Higher Order Logic}:
11.6.1, 11.6.2, 11.6.3 The exercises from Ch 11 focus on defining new
types in HOL and defining the properties and semantics of them. We
then used our new type definitions to develop new theories that can be
imported in further HOL proofs. All of these theories are built using
the Holmake program. Each of the exercises includes a problem
statement, relevant code, test cases as appropriate and test results. 
\end{abstract}

\newpage

\textbf{Acknowledgments}: I received no assistance with this project.

\newpage

\tableofcontents

\newpage

\section{Executive Summary}
\label{sec:executive-summary}

All requirements for this project have been satisfied.  A description of each exercise from Chapter 11 is included in the following chapters.  

A HOLReports subfolder is in the HOL directory with all the HOL generated Latex macros used in the report, the HOL directory contains the exTypeScript.sml and
nexpScript.sml files used by Holmake to generate the theorem object files, and the LaTex directory contains the project report LaTex document.

The theories are shown pretty printed in the Ch. 11 Theory section, and the source code has been included in the Appendix.
\newpage


\section{Chapter 11 Exercises}
\label{sec:chapter-11-exercises}

\subsection{Problem Statement}
\label{sec:problem-statement}
Exercise 11.6.1 Theorem was answered using structural indcution on the inital goal then rewriting
using the APP function definition, the ADD_CLAUSES theorem from arithmeticTheory, and the LENGTH theorem.

Exercise 11.6.2 Theorem used our APP definition along with our Map definition to prove the Map_APP theorem.
Exercise 11.6.3 proofs use our new datatype nexp along with its semantic value definition as well as a few
theories from arithmeticTheory.

\subsection{Test Results}
\label{sec:test-results}

Exercise 11.6.1:
\verbatiminput{../HOL/ex-11-6-1.trans}


Exercise 11.6.2:
\verbatiminput{../HOL/ex-11-6-2.trans}


Exercise 11.6.3:
\verbatiminput{../HOL/ex-11-6-3.trans}

\input{../HOL/HOLReports/HOLnexp}
\input{../HOL/HOLReports/HOLexType}

\newpage

\HOLpagestyle

% ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
\subsection{Exercise 11 Theory}
\label{sec:exercise-11-theory}
\index{exercise11 Theory@\textbf  {exercise11 Theory}}
\begin{flushleft}
\textbf{Built:} \HOLnexpDate \\[2pt]
\textbf{Parent Theories:} indexedLists, patternMatches
\end{flushleft}
% ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

\HOLexTypeTheorems
\HOLnexpTheorems


\HOLindex

\appendix{}

\section{Source Code for exTypeTheory}
\label{sec:source-code-extyp}

The following code is from \emph{HOL/exTypeScript.sml}
\lstinputlisting{../HOL/exTypeScript.sml}

\section{Source Code for nexpTheory}
\label{sec:source-code-nexpth}

The following code is from \emph{HOL/nexpScript.sml}
\lstinputlisting{../HOL/nexpScript.sml}

\end{document}
